HO unification from object language to meta language

### 2024-03-21 paper/main.tex
notazione preliminare
python DSL %SNIP: file, %ENDSNIP

we use math mode for ho.

@@

\begin{elpicode}
kind link type.
type link nat -> nat -> nat -> subst. % link Fo Ho Arity
typeabbrev links list link.
type comp fm -> tm -> links -> links -> subst -> subst -> o.
comp (fcon X) (con X) L L S S.
comp (flam F) (lam G) K L R S :- pi x y\
  (pi A S\ comp x y L L S S) => comp (F x) (G y) K L R S.
comp (fuva M) (uva N []) K [link M N z|K] R S :- new R N S.
comp (fapp[fuva M|A]) (uva N B) K L R S :- distinct A, !,
  fold4 comp A B K K R R,
  new R N S, len A Arity,
  L = [link N M Arity | K].
comp (fapp A) (app B) K L R S :- fold4 comp A B K L R S.
\end{elpicode}

@@

\subsection{Problems with $\eta$}
\otext{The following goal necessita v1 (lo scope è usato):\\ \elpiIn{X = lam x\ lam y\ Y y x, X = lam x\ f}}
\otext{The snd unif pb, we have to unif \elpiIn{lam x\ lam y\ Y x y} with \elpiIn{lam x\ f}}
\otext{It is not doable, with the same elpi var}

@@

>>>>

We use math mode for \Ho.

\begin{tabular}{ll}
  $\lambda x.\lambda y.F_{x y}$ & \elpiIn{lam x\ lam y\ uva F [x, y]} \\
  $f~ a$ &  \elpiIn{app[con "f", con "a"]}\\
  $\lambda x.F_{x} ~ a$ & \elpiIn{lam x\ app[uva F [x], con "a"]} \\
  $\lambda x.F_{x} ~ x$ & \elpiIn{lam x\ app[uva F [x], x]} \\
\end{tabular}

@@

\input{code/comp_base_types}
\input{code/comp_base}

@@

\subsection{Problems with $\eta$}

\input{code/comp_eta}

\otext{The following goal necessita v1 (lo scope è usato):\\ \elpiIn{X = lam x\ lam y\ Y y x, X = lam x\ f}}
\otext{The snd unif pb, we have to unif \elpiIn{lam x\ lam y\ Y x y} with \elpiIn{lam x\ f}}
\otext{It is not doable, with the same elpi var}

@@

\input{code/comp_beta}
